Commutative Character Sheaves

### 2015-11-12 followup.tex
One lemma left in Section 3 . . . .

The first step in this process is to rule out character sheaves as above.
The following proposition will be proven in Section \ref{sec:descent}.
\begin{proposition} \label{prop:Gder_triv}
Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $\cs{L} \cong q^*(\cs{L}\ab)$ for some
character sheaf $\cs{L}\ab$ on $G\ab$.
\end{proposition}

@@

Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines
\[
\begin{tikzcd}
m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{r}{c = m \circ (m \times (i \circ m \circ \theta))} & c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der} \arrow{r} & (\EE)_G\otimes (\EE)_G.
\end{tikzcd}
\]
Using the monadic structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
\[
\begin{tikzcd}
m^*\cs{L} \arrow{r}  & (\theta^* m^* i^*\cs{L})^\vee.
\end{tikzcd}
\] 
Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
\[
\begin{tikzcd}
\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
\end{tikzcd}
\]

@@

@@

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\begin{equation}\label{eq:nu}
\begin{tikzcd}
\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\end{equation}
and $s^*(\nu) = \id_{\cs{L}}$.
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{eq:alphanu}
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
\begin{equation}\label{eq:alphanu}
\begin{tikzcd}
\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
\end{tikzcd}
\end{equation}
commutes.
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

\begin{lemma}\label{lem:GderGder}
If $(\cs{L},\mu,\beta)$ is a commutative character sheaf on $G$ then $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is a morphism of $G\der\times G\der$-equivariant linear character sheaves on $G\times G$.
\end{lemma}

\begin{proof}
\end{proof}

@@

Now suppose $q : G \to Q$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
Q
\end{tikzcd}
\]
Let $\cs{L}$ be a linear character sheaf on $Q$.
Consider the functor
\[
q^* : \CS(Q) \to \CS(G)
\]
given on objects by $(\cs{L},\mu) \mapsto (q^*\cs{L}, (q\times q)^* \mu)$; cf [Dictionary].
Then $q^*\cs{L}$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
\[
\nu : a^* q^* \cs{L} \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L} = (q\circ p)^*\cs{L} \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
\]
This simple observation defines the comparison functor
\[
q_H^* : \CS(Q) \to CS_H(G)
\]
and shows that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(Q) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]

@@

\subsection{Closed subgroups}

We now suppose that $i : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
Then we have the diagram
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
\end{tikzcd}
\]
where $f(h,g) = (i(h),g)$.
% (a(h,g) g^{-1}, g) = (h,g)$.
%Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
Then every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\[
\nu = (\beta \boxtimes \id) \circ  f^*\mu,
\] 
or more precisely, by the following diagram of isomorphisms.
\[
\begin{tikzcd}
\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul}{p= p_1} \\ 
& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_\circ f = i}[swap]{p_2\circ f = \id}  & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2}.

\begin{lemma}\label{lem:beta}
$\CS_H(G)$ is equivalent to the category $\CS'(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
\end{lemma}

\begin{proof}
\end{proof}

\subsection{Proofs for results from Section \ref{sec:defs}}

@@

\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
Now,
\[
\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r} & G\der \arrow{r}{i} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]
gives
\[
\begin{tikzcd}
\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
%
Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
it now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{G\der}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
%that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ if and only if $\cs{L} = q^*\cs{L}\ab$ for some $\cs{L}\ab \in \CS(G\ab)$.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$. 
\[
\begin{tikzcd}
\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} \arrow{dl} \\
\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu} & \arrow{u}  \CCS_{G\der}(G) & 
\end{tikzcd}
\]
The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{G\der}(G) \to \CS'(G)$ is $\CCS(G)$.
To that end, suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{ssec:comcom}.
Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncom}.
Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
in particular $\gamma = (q\times q)^* \xi$.

Using Lemmas~\ref{lem:HH} and \ref{lem:GderGder}, we may interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
It now follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$, completing the proof of Theorem~\ref{thm:Gab}.
\end{proof}

>>>>

The first step in this process is to rule out character sheaves as above.
The following proposition will be proven in Section \ref{ssec:proofs}.
\begin{proposition} \label{prop:Gder_triv}
Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $\cs{L} \cong q^*(\cs{L}\ab)$ for some
character sheaf $\cs{L}\ab$ on $G\ab$.
\end{proposition}

@@

Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines
\[
\begin{tikzcd}
m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{r}{c = m \circ (m \times (i \circ m \circ \theta))} & c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der} \arrow{r} & (\EE)_G\otimes (\EE)_G.
\end{tikzcd}
\]
Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
\[
\begin{tikzcd}
m^*\cs{L} \arrow{r}  & (\theta^* m^* i^*\cs{L})^\vee.
\end{tikzcd}
\] 
Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
\[
\begin{tikzcd}
\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
\end{tikzcd}
\]

@@

The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given in Section~\ref{ssec:proofs}, with the proof of Theorem~\ref{thm:Gab}.

@@

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=1]{r}{a}
\arrow[shift right=1]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\begin{equation}\label{eq:nu}
\begin{tikzcd}
\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\end{equation}
and $s^*(\nu) = \id_{\cs{L}}$, where $s : G\to H\times G$ is given by $s(g) = (1,g)$.
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{eq:alphanu}
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
\begin{equation}\label{eq:alphamu}
\begin{tikzcd}
\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
\end{tikzcd}
\end{equation}
commutes.
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

@@

Now suppose $q : G \to Q$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=1]{r}{a}
  \arrow[shift right=1,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
Q
\end{tikzcd}
\]
Let $\cs{L}$ be a linear character sheaf on $Q$.
Consider the functor
\[
q^* : \CS(Q) \to \CS(G)
\]
given on objects by $(\cs{L},\mu) \mapsto (q^*\cs{L}, (q\times q)^* \mu)$; cf [Dictionary].
Then $q^*\cs{L}$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
\[
\nu : a^* q^* \cs{L} \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L} = (q\circ p)^*\cs{L} \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
\]
This simple observation defines the comparison functor
\[
q_H^* : \CS(Q) \to CS_H(G)
\]
and shows that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(Q) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]

@@

\subsection{Closed subgroups}\label{ssec:closed}

We now suppose that $i : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
Then we have the diagram
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
\end{tikzcd}
\]
where $f(h,g) = (i(h),g)$.
% (a(h,g) g^{-1}, g) = (h,g)$.
%Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\[
\nu = (\beta \boxtimes \id) \circ  f^*\mu,
\] 
or more precisely, by the following diagram of isomorphisms.
\[
\begin{tikzcd}
\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul}{p= p_1} \\ 
& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_\circ f = i}[swap]{p_2\circ f = \id}  & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The next lemma makes that statement more precise.

\begin{lemma}\label{lem:beta}
$\CS_H(G)$ is equivalent to the category $\CS^H(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
\end{lemma}

\begin{proof}
We have seen how every $(\cs{L},\mu,\nu)\in \CS_H(G)$ determines an isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$.
This isomorphism is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2} as they apply to $\nu : a^*\cs{L}\to p^*\cs{L}$. 
It is straightforward but quite unpleasant matter to show that those conditions are exactly equivalent to the condition that the isomorphism Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
\end{proof}

\subsection{Proofs for results from Section \ref{sec:defs}}\label{ssec:proofs}

@@

\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
Now,
\[
\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r} & G\der \arrow{r}{i} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]
gives
\[
\begin{tikzcd}
& \CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
\CS^{G\der}(G) & \arrow[equal]{l} \CS'(G) \arrow{u}{\text{forget}}  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
%
Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncom} and the observation that it is precisely the category $\CS^{G\der}(G)$, taking the case $H=G\der$ in Section~\ref{ssec:closed}.
Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
it now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{G\der}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
%that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ if and only if $\cs{L} = q^*\cs{L}\ab$ for some $\cs{L}\ab \in \CS(G\ab)$.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{G\der}(G) \to \CS'(G)$ is $\CCS(G)$.
\[
\begin{tikzcd}
\CS(G\der) 
& \arrow{l}[swap]{i^*} \CS(G) 
&\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} 
&  \CS_{G\der}(G) \arrow{u}{\text{forget}}  
&  \arrow[bend left=35pt, dashed]{dll} \CCS(G\ab) \arrow{u} \arrow{dl} \\
\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu} 
& \arrow{u}  \CCS_{G\der}(G) 
& 
\end{tikzcd}
\]

Suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{ssec:comcom}.
Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncom}.
Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
in particular $\gamma = (q\times q)^* \xi$.
Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$, completing the proof of Theorem~\ref{thm:Gab}.
This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
\end{proof}
